---
author: ""
header-includes:
   - \usepackage{rotating}
   - \usepackage{float}
   - \usepackage{natbib}
   - \usepackage{booktabs}
   - \usepackage{xcolor}
geometry: "left=1cm,right=1cm,top=0.9cm,bottom=1.2cm"

output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    number_sections: true
bibliography: ref.bib
link-citations: yes
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
library(rio)
library(latex2exp)
library(dplyr)
library(tibble)
library(ggplot2)
library(lubridate)
library(data.table)
library(knitr)
library(kableExtra)
library(haven)
library(tidyr)
library(tidyverse)
library(stargazer, quietly = TRUE)
library(plm) 
library(xtable)
library(RColorBrewer)
library(ggrepel)
library(ggpmisc)
library(scales)
library(lmtest)
t1 <- readRDS("output_table1.Rds")
t2 <- readRDS("output_table2.Rds")
plot_data <- readRDS("output_plot_sample.Rds")
```

This table validates the magnitude of the calculated ICCs. We compare our replicated Median ICC against the reported values in the original paper for select years.
```{r table1, echo = FALSE, fig.cap="Figure", fig.topcaption=TRUE, results = 'asis', warning=FALSE, message=FALSE}
display_years <- c(1985, 1990, 1995, 2000, 2005, 2008, 2010)
t1_display <- t1[Year %in% display_years]

# Formatting
t1_display %>%
  kable(caption = "Replication of Table 1 Panel A: Summary Statistics",
        col.names = c("Year", "N Firms", "Median ICC (%)", "Q1 (%)", "Q3 (%)", "Std Dev", "Paper Target (%)"),
        digits = 1,
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  column_spec(7, bold = TRUE, color = "blue") # Highlight the target column
```

We regress Cash Flow News (CF) and Discount Rate News (DR) on realized returns at various horizons (k)
\[\beta_{CF} = \frac{Cov(CF_k, Ret_k)}{Var(Ret_k)}\]
As the horizon k increases, cash flows should explain a larger proportion of return variation.
```{r table2, echo = FALSE, fig.cap="Figure", fig.topcaption=TRUE, results = 'asis', warning=FALSE, message=FALSE}
t2 %>%
  dplyr::select(-Obs) %>%
  kable(caption = "Replication of Table 2 Panel B: Variance Decomposition",
        col.names = c("Horizon (Months)", "Beta CF (Our Result)", "Beta DR", "Paper Target (Beta CF)"),
        digits = 3,
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  column_spec(2, bold = TRUE) %>%
  column_spec(4, bold = TRUE, color = "blue")
```

```{r table3, echo = FALSE, fig.cap="Figure", fig.topcaption=TRUE, results = 'asis', warning=FALSE, message=FALSE, fig.width = 6, fig.height = 3}
ggplot(plot_data, aes(x = Ret_12m, y = CF_12m)) +
  geom_point(alpha = 0.1, color = "darkblue", size = 0.8) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black") +
  labs(title = "1-Year Horizon: Returns vs. Cash Flow News",
       subtitle = "Red Line = Regression Fit | Dashed Line = 45 Degree (Perfect Match)",
       x = "Realized Return (12 Months)",
       y = "Cash Flow News (12 Months)") +
  theme_minimal() +
  coord_cartesian(xlim = c(-1, 1), ylim = c(-1, 1)) # Zoom in on the core data
```